Fractional anisotropy as a tracer of cosmic voids

### 2014-10-24 cosmic_voids.tex
New profiles of density and velocity. Removing density-watershed method

This paper is organized as follows. In section 2 we describe the used
simulation for testing our void finding algorithm, i.e. the Bolshoi
simulation. Alternatively to the web schemes Tweb and Vweb, we propose 
a heuristic web classifier based on three thresholds of the density field. 
This is used in order to illustrate the differences of our scheme with a
density-based classifier. A detailed description of these methods is 
presented in section 3. In section 4 we describe how the FA can be used 
for tracing the structure of voids. Once obtained meaningful catalogues 
of voids for each scheme, we proceed to compare some typical and general 
interest properties of voids such as volume functions, distributions of 
size and density and velocity profiles. This is done in section 5. Finally 
in section 6 we analyse and evaluate our findings.

@@

%-------------------------------------------------------------------------
\subsection{The density-based web finder}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

Although the density field is a key quantity for understanding the 
large-scale Universe, the filamentary structure of the Cosmic Web is 
poorly traced by it (see e.g. Fig. \ref{fig:FA_field}). In order to 
compare our new proposal based on the the fractional anisotropy as a 
tracer field of voids, we define a very basic approach for environmental 
finding based on three thresholds of the density field.

%.........................................................................
%Table with volume filling fraction
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{c  c  c  c c} \hline\hline
	\textbf{Volume}  &				&\textbf{Scheme}& \\
	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
	\textbf{Fraction}&\textbf{Tweb}&\textbf{Vweb}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
	Sheets		     &	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	      &	$0.60$				\\
	Filaments		 &	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 		  &	$8.82$				\\
	Knots			 &	$0.75\%$	&	$1.22\%$	&	$0.98\%$  		  &	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small VFF for each type of environment and for each
  web scheme. VFF for the density-based scheme are defined as the 
  arithmetic mean of the Tweb and the Vweb. The last column corresponds 
  to the threshold values in the density field in order to obtain the 
  required VFF. Note there is not any value associated to knots as there 
  is not a higher order environment.}

  \label{tab:VFF}
\end{center}
\end{flushleft}
\end{table}
%.........................................................................

In next section we shall describe an alternative approximation to select 
the threshold value $\lambda_{th}$. One of the main results is the similar 
volume filling fraction (VFF) for each environment in both web schemes 
(see Fig. \ref{fig:VFF}). Using this result, we propose here a heuristic 
classification of the Cosmic Web based on three density thresholds 
assigned to each boundary (i.e. void-sheet, sheet-filament and 
filament-knot)\footnote{The progressive sequence void-sheet-filament-knot 
along any path through the Cosmic Web should be always satisfied as each 
used field is smoothed.} such that the corresponding VFF values are 
similar to the values obtained for the Tweb and the Vweb, specifically 
they are defined to be the arithmetic mean of both schemes.

@@

%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} } }
%.........................................................................
where the eigenvalues are taken from either the Tweb or the Vweb 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
corresponds with a isotropic dynamic and $FA=1$ with a highly anisotropic 
distribution.

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes and the logarithmic density field over a slide of the 
simulation. Some important points can be concluded of this figure.

%.........................................................................
\begin{itemize}
\item Voids display a highly isotropic expanding dynamic at their centres, 
becoming gradually more anisotropic at outer regions.
\item Knots feature with very isotropic collapses. For the Tweb, the FA 
exhibits very narrow distribution around knots whereas for the Vweb, these
distributions are more spread out, thereby indicating strong differences 
between the density and the velocity fields in highly non-linear regions.
\item The filamentary structure of the Cosmic Web is very good traced by
high FA values (black regions), thus indicating very anisotropic dynamics 
for sheets and filaments.
\item The density field poorly traces the Cosmic Web. This is a somehow 
expected result due to the semi-infinite range of the density field, what 
makes more difficult to trace structures.
\end{itemize}
%.........................................................................

@@

%.........................................................................
%FIGURE 1: Volume Filling Fractions for environs
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

  \captionof{figure}{\small Volume Filling Fraction for each type of 
  environment with respect to the chosen threshold $\lambda_{th}$ for both
  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
  threshold value is chosen such that the fractional anisotropy along the 
  void-sheet boundaries has a median value of $FA=0.95$.}

  \label{fig:VFF}
  \vspace{0.1 cm}

@@

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \vspace{0.1 cm}  
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_density.pdf}

@@

%.........................................................................
%FIGURE 6: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}

@@

  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_VwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}

>>>>

This paper is organized as follows. In section 2 we describe the used
simulation for testing our void finding algorithm, i.e. the Bolshoi
simulation. A detailed description of these methods is presented in 
section 3. In section 4 we describe how the FA can be used for tracing the 
structure of voids. Once obtained meaningful catalogues of voids for each 
scheme, we proceed to compare some typical and general interest properties 
of voids such as volume functions, distributions of size and density and 
velocity profiles. This is done in section 5. Finally in section 6 we 
analyse and evaluate our findings.

@@

@@

%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} } }
%.........................................................................
where the eigenvalues are taken from either the Tweb or the Vweb 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
corresponds with an isotropic dynamic and $FA=1$ with a highly anisotropic 
distribution.

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes and the logarithmic density field for a slide of the 
simulation. Some important points can be concluded of this figure.

%.........................................................................
\begin{itemize}
\item Voids display a highly isotropic expanding dynamic at their centres, 
becoming gradually more anisotropic at outer regions.
\item Knots feature with very isotropic collapses. For the Tweb, the FA 
exhibits very narrow distribution around knots whereas for the Vweb, these
distributions are more spread out, thereby indicating strong differences 
between the density and the velocity fields in highly non-linear regions.
\item The filamentary structure of the Cosmic Web is very well traced by
high FA values (black regions), thus indicating very anisotropic dynamics 
for sheets and filaments.
\item The density field poorly traces the Cosmic Web. This is a somehow 
expected result due to the semi-infinite range of the density field, what 
makes more difficult to trace structures.
\end{itemize}
%.........................................................................

@@

%.........................................................................
%FIGURE 1: Volume Filling Fractions for environs
%\begin{flushleft}
%\begin{figure*}
%\centering
%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}  
%  
%  \captionof{figure}{\small Volume Filling Fraction for each type of 
%  environment with respect to the chosen threshold $\lambda_{th}$ for both
%  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
%  threshold value is chosen such that the fractional anisotropy along the 
%  void-sheet boundaries has a median value of $FA=0.95$.}
%
%  \label{fig:VFF}
%  \vspace{0.1 cm}
%
%\end{figure*}
%\end{flushleft}
%.........................................................................

@@

  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \vspace{0.1 cm}
  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \vspace{0.1 cm}  
%  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
%  width=0.73\textheight]{./figures/cosmicweb_density.pdf}

@@

%.........................................................................
%FIGURE 6: Density profile of voids for each defined scheme
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_density_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_density_VwebFAG.pdf}
%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
%  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}

@@

  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_velocity_TwebFAG.pdf}
  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_velocity_VwebFAG.pdf}
%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
%  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}
